### 2007-01-15 Documentation/part1.tex
*** empty log message ***

Gold + Silver & {\tt NF\_Goldsilver.glb} & as {\tt NFvar.glb} 
plus 5~kt ECC detector for Silver Channel
measurement & \cite{Huber:2002mx,Huber:2006wb,Autiero:2003fu} \\[0.2cm]

>>>>

Gold + Silver & {\tt NF\_GoldSilver.glb} & as {\tt NFvar.glb} 
plus 5~kt ECC detector for Silver Channel
measurement & \cite{Huber:2002mx,Huber:2006wb,Autiero:2003fu} \\[0.2cm]
